---
title: "Assessing the Impacts of Economic Factors on Funding for Tech Startups"
author: "Nana Adjoa Ansah, Parunjodhi Munisamy, Michel Ruiz-Fuentes"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8,
                      echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```


```{r loading-packages}
#loading in packages

library(tidyverse)
library(broom)
library(ggplot2)
library(rio)
library(ggpubr)
library(moderndive)
library(car)
library(stargazer)
library(vtable)
```

#Funding amount as a dependent variable

1) Funding amount which is our dependent variable with unit USD. It is a continuous variable. When plotting a histogram of this parameter, the distribution is found to be very right skewed.\

```{r dependent-variable, results = FALSE}
#transforming funding amount from a discrete variable into a continuous variable

research_data$`funding_amount` <- as.numeric(as.character(research_data$`Funding Amount (USD)`))
```


```{r dependent-variable, fig2, fig.height = 4, fig.width = 6, fig.align = "center"}
#Plotting a histogram of funding amount
research_data %>%
  ggplot(aes(x = funding_amount)) +
  geom_histogram() + 
  labs(
    title = "Distribution of Funding Amount",
    subtitle = "Containing all Funding Stages",
    x = "Funding Amount (in USD)",
    y = "Count"
  ) +
  scale_x_continuous(labels = scales::dollar)
```

The highest funding amounts are private equity and unknown and skew our distribution significantly. Since private equity is not a funding stage and the unknowns do not bring insights, we can remove these two funding stages from our data without creating bias. This reduces the skewness of the distribution.\

```{r, fig3, fig.height = 4, fig.width = 6, fig.align = "center"}
#Reducing the skewness of the distribution by omitting the 'unknown' and 'private equity' variables

research_data <- research_data %>%
  filter(!`Funding Stage` == "Unknown") %>%
  filter(!`Funding Stage` == "Private Equity") 

research_data %>%
  ggplot(aes(x = funding_amount)) +
  geom_histogram() + 
  labs(
    title = "Distribution of Funding Amount",
    subtitle = "Removing Private Equity and Unknown",
    x = "Funding Amount (in USD)",
    y = "Count"
  ) +
  scale_x_continuous(labels = scales::dollar)
```

The data is still skewed so we will transform funding amount values in an attempt to have a uniform distribution using two approaches: standardization and log transformation.\

##Transforming the variable funding amount for a uniform distribution
```{r standardized-dv}
#standardization of the funding amount variable

research_data$funding_amt_std <- scale(research_data$funding_amount, center = T, scale = T)
```

```{r log-dv}
#log transformation of the funding amount variable

research_data$funding_amt_log <- log(research_data$funding_amount)
```

```{r, fig4, fig.height = 4, fig.width = 6, fig.align = "center"}
#plotting a histogram of the standardized variable funding amount
std_funding_amt <- research_data %>%
  ggplot(aes(x = funding_amt_std)) +
  geom_histogram() + 
  labs(
    title = "Distribution of Standardized \nFunding Amount",
    x = "Standardized Funding Amount",
    y = "Count"
  )
```

```{r, fig5, fig.height = 4, fig.width = 6, fig.align = "center"}
#plotting a histogram of the log transformed variable funding amount
log_funding_amt <- research_data %>%
  ggplot(aes(x = funding_amt_log)) +
  geom_histogram() + 
  labs(
    title = "Distribution of Log of Funding \nAmount",
    x = "Log of Funding Amount",
    y = "Count"
  )
```

```{r log-std-dv, fig5, fig6, fig.height = 4, fig.width = 6, fig.align = "center"}
ggarrange(std_funding_amt, log_funding_amt,
          ncol = 2)
```

Looking at the transformation plots above, there is a more uniform distribution for funding amount in the log transformation with less of a skew and more linearity.
